\LARGE \bf Informed sampling by Markov chain Monte Carlo methods

### 2017-01-24 paper.tex
added refs
add bst
starting intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\section{Related work}
\subsection{planning}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
They search through the continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
Vertices and edges in $G$ correspond to collision-free states and paths, respectively.

Roughly speaking, all these algorithms iteratively sample new states.
This is required to ensure that, as the number of samples tends to infinity, 
(i)~a solution will be found 
(a property called \emph{probabilistic completeness})
and that
(ii)~given some optimization criteria, the quality of the solution will progressively converge to the quality of the optimal solution
(a property called \emph{asymptotic  optimality}).

While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.

In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
Indeed, 
However, recent years 
Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{•}

\section{Related work}
\subsection{planning}
Classic:\\
RRT~\cite{LK01}

PRM~\cite{KSLO96}

AO:\\
RRT*, PRM*~\cite{KF11}

BIT*~\cite{GSB15}

FMT*~\cite{JSCP15}

Near AO:\\
LBT-RRT~\cite{SH16}

SPARSE~\cite{DB14}

RGGS~\cite{SSH16}

Kinodynamic works:\\~\cite{SL14, XBPA15, WB13, KF10}
